A semantics of core AUTOSAR

### 2016-08-30 paper/paper.tex
Tweaks.

The formal semantics may also lay the foundation of tools that analyze or transform AUTOSAR models. One such example is our AUTOSAR simulator \cite{ARSim}, which interprets AUTOSAR models entirely on basis of the transition system, utilizing truly random scheduling and a maximum progress assumption to select among available transitions at each step. The benefit of this simulator is its ability to dynamically execute AUTOSAR Software Component models as they are, without prior selection of a particular platform or translation into a low level C representation. A further avenue of exploration concerns the potential to prove properties of AUTOSAR system on basis of their semantics. To prepare for this opportunity, we have defined the transition system used in this paper as a Horn clause file readable by common theorem provers \cite{AR.eprover}, and in fact produced Appendix~\ref{sec:Rules} through a simple formatting translation of this file.

>>>>

The formal semantics may also provide a foundation for tools that analyze or transform AUTOSAR models. One such example is our AUTOSAR simulator \cite{ARSim}, which interprets AUTOSAR models entirely on basis of the transition system, utilizing truly random scheduling and a maximum progress assumption to select among available transitions at each step. The benefit of this simulator is its ability to dynamically execute AUTOSAR Software Component models as they are, without prior selection of a particular platform, or translation into a low level representation. A further avenue of exploration concerns the potential of proving properties of AUTOSAR system on basis of their semantics. To prepare for this opportunity, we have defined the transition system used in this paper as a Horn clause file readable by common theorem provers, and in fact produced Appendix~\ref{sec:Rules} through a simple formatting translation of this file \cite{AR.eprover}.
